\documentclass[12pts]{article}

% pseudo Times New Roman
\usepackage{mathptmx}% http://ctan.org/pkg/mathptmx
% margins 1 in
\usepackage[a4paper, margin=1in]{geometry}
%line space
\renewcommand{\baselinestretch}{1.5}
% APA citations
\usepackage{apacite}
% math symbols
\usepackage{amssymb}
% tables created in rmd
\usepackage{longtable}
%math 
\usepackage{amsmath}
%images 
\usepackage{graphicx}
\usepackage{subcaption}

%opening
\title{QUANTAL RESPONSE EQUILIBRIUM IN A CITIZEN-CANDIDATE EXPERIMENT}
\author{Alexander Elbittar \and Andrei Gomberg \and Dario Trujano Ochoa}
\date{2018}

\begin{document}

\maketitle

\begin{abstract}

In this study, a Citizen-Candidate model of political competition was implemented in an experiment and the Quantal Response Equilibrium (QRE) was adjusted to data. 
This model of elections is based in the Hotelling-Downs model of spatial competition. 
However, candidates do not choose location, which in this case was their own ideal point, but to campaign or not. QRE is a generalization of the Nash equilibrium (NE) and player's responses are random. Six experimental conditions combine two entry cost levels, 
two voting systems (plurality rule and run-off), and three set of ideal points. 
The Nash Equilibrium (NE) is a good ex ante prediction in all games. 
Though, it cannot predict the large rate of participation nor the changes related to costs and ideal positions.  
In summary,  experimental  data  was explained  by QRE which assumes  a  stochastic  non-perfect  maximizing  decision rule when adjusted by game. However, in one game, the parameter that measures maximizing behavior was high compared with other games.


\end{abstract}

\input{intro}

\input{model}

\input{DesignPredictions}

\input{results_QRE}

\input{concl}

\bibliographystyle{apacite} 

\bibliography{library}

\end{document}
